%\begin{remark}
%\label{Result:Rem:6}
\paragraph*{}A sketch of the proof for Theorem \ref{Result:Theorem:1} is given here. In the first step, we try to bound the probability of arm elimination of any sub-optimal arm without cluster elimination. This is shown in Proposition \ref{proofSketch:Prop:1}. By simply taking $p=1$ we can achieve arm elimination without any cluster elimination. In second step, we try to bound the probability of cluster elimination(without any arm elimination) with all arms within it.  A slight modification to the algorithm allows us to do this. By taking $p>1$, removing the arm elimination condition, stopping when we are just left with one cluster and pulling the $max\lbrace \hat{r}_{i}\rbrace$, where $a_{i}\in B_{m}$ we can achieve this.  This is shown in Proposition \ref{proofSketch:Prop:2}. Finally in step three, in the proof of Theorem \ref{Result:Theorem:1} we combine both arm elimination and cluster elimination to get the regret upper bound.  
%\end{remark}
	

\begin{proposition}
\label{proofSketch:Prop:1}
Considering only the arm elimination condition and $p=1$ the total regret till $T$ is upper bounded by $\E [R_{T}]\leq \sum\limits_{i\in A:\Delta_{i}\geq b}\bigg\lbrace\bigg(\dfrac{2^{1+4\rho_{a}}\rho_{a}^{2\rho_{a}}T^{1-\rho_{a}}}{\psi^{\rho_{a}}\Delta_{i}^{4\rho_{a}-1}}\bigg) + \bigg(\Delta_{i}+\dfrac{32\rho_{a}\log{(\psi T\dfrac{\Delta_{i}^{4}}{16\rho_{a}^{2}})}}{\Delta_{i}}\bigg)  +  \bigg(\dfrac{T^{1-\rho_{a}}\rho_{a}^{2\rho_{a}}2^{2\rho_{a}+\frac{3}{2}}}{\psi^{\rho_{a}}\Delta_{i}^{4\rho_{a} -1}} \bigg) \bigg \rbrace+\sum\limits_{i\in A:0\leq\Delta_{i}\leq b}\bigg(\dfrac{T^{1-\rho_{a}}\rho_{a}^{2\rho_{a}}2^{2\rho_{a}+\frac{3}{2}}}{\psi^{\rho_{a}}b^{4\rho_{a} -1}} \bigg) + max_{i:\Delta_{i}\leq b}\Delta_{i}T$ for all $b\geq\sqrt{\dfrac{e}{T}}$, where $\rho_{a}\in (0,1]$ is the arm elimination parameter, $\psi$ is the exploration regulatory factor, $p$ is the number of clusters and $T$ is the horizon.
\end{proposition}


	The proof of Proposition 1 is given in Appendix \ref{App:A}.(Supplementary material).

%\begin{remark}
%\label{Result:Rem:7}	
\paragraph*{} Thus, we see that the confidence interval term $c_{m}=\sqrt{\dfrac{\rho_{a}\log (\psi T\epsilon_{m}^{2})}{2 n_{m}}}$ makes the algorithm eliminate an arm $a_{i}$ as soon as $\sqrt{\rho_{a}\epsilon_{m}}<\dfrac{\Delta_{i}}{2}$. The above result is in contrast with UCB-Improved which only deletes an arm if $\tilde{\Delta}_{m}<\dfrac{\Delta_{i}}{2}$, where $\tilde{\Delta}_{m}$ is initialized at $1$ and is halved after every round. We also point out here that when $c_{m}=\sqrt{\dfrac{\rho_{a}\log (\psi T\epsilon_{m}^{2})}{2 n_{m}}}$ and $\rho_{a}$ is decreased after every round, then an arbitrary arm $a_{i}$ is removed as soon as  $\sqrt{\rho_{a}\epsilon_{m}}<\dfrac{\Delta_{i}}{2}$ which essentially makes it a faster elimination procedure than UCB-Improved if $\rho_{a}\leq \epsilon_{m}$.
%\end{remark}


\begin{corollary}
\label{proofSketch:Corollary:1}
For $\rho_{a}=1$ in the result of proposition $1$, $\sum\limits_{i\in A:\Delta_{i}\geq b}\bigg\lbrace\bigg(\dfrac{2^{1+4\rho_{a}}\rho_{a}^{2\rho_{a}}T^{1-\rho_{a}}}{\psi^{\rho_{a}}\Delta_{i}^{4\rho_{a}-1}}\bigg) + \bigg(\Delta_{i}+\dfrac{32\rho_{a}\log{(\psi T\dfrac{\Delta_{i}^{4}}{16\rho_{a}^{2}})}}{\Delta_{i}}\bigg)  +  \bigg(\dfrac{T^{1-\rho_{a}}\rho_{a}^{2\rho_{a}}2^{2\rho_{a}+\frac{3}{2}}}{\psi^{\rho_{a}}\Delta_{i}^{4\rho_{a} -1}} \bigg) \bigg \rbrace+\sum\limits_{i\in A:0\leq\Delta_{i}\leq b}\bigg(\dfrac{T^{1-\rho_{a}}\rho_{a}^{2\rho_{a}}2^{2\rho_{a}+\frac{3}{2}}}{\psi^{\rho_{a}}b^{4\rho_{a} -1}} \bigg) + max_{i:\Delta_{i}\leq b}\Delta_{i}T$ we get a regret bound of $\sum\limits_{i\in A:\Delta_{i}\geq b}\bigg(\Delta_{i} + \dfrac{44}{\psi(\Delta_{i})^{3}} + \dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}}\bigg) + \sum\limits_{i\in A:0\leq\Delta_{i}\leq b}\dfrac{12}{\psi b^{3}}$ for using just arm elimination with $p=1$.
\end{corollary}


\begin{proof}
In the result of Proposition $1$ if we take $\rho_{a}=1$ then the regret bound becomes $ \sum\limits_{i\in A:\Delta_{i}\geq b}\bigg(\Delta_{i} + \dfrac{44}{\psi(\Delta_{i})^{3}} + \dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}}\bigg) + \sum\limits_{i\in A:0\leq\Delta_{i}\leq b}\dfrac{12}{\psi b^{3}}$. From the result we can see that for small $\Delta_{i}$ and large $K$, the terms like $ \sum_{i\in A:\Delta_{i}\geq b}\bigg(\dfrac{44}{\psi(\Delta_{i})^{3}}\bigg) + \sum_{i\in A:0\leq\Delta_{i}\leq b}\dfrac{12}{\psi b^{3}}$ can become the dominant term in the regret rather than $\sum_{i\in A:\Delta_{i}\geq b}\dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}}$. Intuitively, this actually suggests that the algorithm is trying to eliminate arms with too low exploration and so the probability of elimination is low and error(risk) is high. For this essentially we introduce $\rho_{a},\rho_{s}$ and $\psi$ and by carefully defining their values enables us to eliminate arms and clusters aggressively and thereby reduce those two terms. 
\end{proof}

\begin{proposition}
\label{proofSketch:Prop:2}
Considering only the cluster elimination condition and $p>1$, the total regret till $T$ is upper bounded by $\E [R_{T}]\leq \sum\limits_{i\in A:\Delta_{i}\geq b}\bigg\lbrace \bigg(\dfrac{2^{2+4\rho_{s}}\rho_{s}^{2\rho_{s}}T^{1-\rho_{s}}}{\psi^{\rho_{s}}\Delta_{i}^{4\rho_{s}-1}}\bigg) + \bigg(\Delta_{i}+\dfrac{32\rho_{s}\log{(\psi T\dfrac{\Delta_{i}^{4}}{16\rho_{s}^{2}})}}{\Delta_{i}}\bigg)  +  \bigg(\dfrac{T^{1-\rho_{s}}\rho_{s}^{2\rho_{s}}2^{2\rho_{s}+3}}{\psi^{\rho_{s}}\Delta_{i}^{4\rho_{s} -1}} \bigg)\bigg \rbrace +\sum\limits_{i\in A:0\leq\Delta_{i}\leq b}\bigg(\dfrac{T^{1-\rho_{s}}\rho_{s}^{2\rho_{s}}2^{2\rho_{s}+3}}{\psi^{\rho_{s}}b^{4\rho_{s} -1}} \bigg) + max_{i:\Delta_{i}\leq b}\Delta_{i}T$ for all $b\geq \sqrt{\dfrac{e}{T}}$, where $\rho_{s}\in (0,1]$ is the cluster elimination parameter, $\psi$ is the exploration regulatory factor, $p$ is the number of clusters and $T$ is the horizon.
\end{proposition}

	The proof of Proposition 2 is given in Appendix \ref{App:B}.(Supplementary material)
